---
title: "EDS212 Day 4 Comp 2"
format: html
editor: visual
---

## Data Exploration

General Notes:

-   Best practice, use the skimr package

-   Start with head() and skim() functions to get quick snapshots of the initial data and initial summary statistics

```{r}
library(GGally)
library(skimr)
library(palmerpenguins)
library(tidyverse)
```

First things first: Let's look at the dataset

```{r}
view(penguins)
## We don't want this in our actual code because it is not best practice. Use the function head to get a snapshot of the first n lines of the data!
```

**Basics:**

-   names: get variable names

-   dim: get data dimensions

-   head: get first n lines (6 by default) \*\*Best practice, always start with this

-   tail: get last n lines (6 by default)

-   summary: get basic summary statistics

```{r}
names(penguins)
dim(penguins)
head(penguins)
tail(penguins)
summary(penguins)
```

```{r}
## Using skim! Great for initial data exploration
skim(penguins)
```

```{r}
## If we want to look at a snapshot of relationships between variables with mini graphs, we can use the function ggpairs 
ggpairs(penguins)
```
